### 2014-02-05  feature-selection-high-recall/FeatureSelectionProject/doc/fs_hr/empirical.tex
Update

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table*}[tbp!]
\centering
\begin{tabular}{|l|r|r|r|r|l|} \hline
Dataset & \# Features & \# Data & \# Features/\# Data & \% True Labels & Feature Type\\ \hline \hline 
Breast Cancer	& 9	& 699	& 0.013	& 34 \%	& All Numeric\\ \hline
Diabetes        & 8	& 768	& 0.010	& 35 \%	& All Numeric\\ \hline
Heart Statlog	& 13	& 270	& 0.048	& 44 \%	& All Numeric\\ \hline
Spect	        & 22	& 80	& 0.275 & 33 \%	& Categorical\\ \hline
Vote	        & 16	& 435	& 0.037	& 39 \%	& Categorical\\ \hline
Newsgroup	& 500	& 1963	& 0.255	& 49 \%	& All Binary\\ \hline
Horse Colic	& 22	& 368	& 0.060	& 37 \%	& Categorical (16) and numeric (6)\\ \hline
Credit-American	& 15	& 690	& 0.022	& 44 \%	& Categorical(9) and numeric (6)\\ \hline
Credit-German	& 20	& 1000	& 0.020 & 30 \%	& Categorical (13) and Numeric (7)\\ \hline
Hepatitis	& 19	& 155	& 0.123	& 21 \%	& Categorical (13) and Numeric (6)\\ \hline
Ionosphere	& 34	& 351	& 0.097	& 36 \%	& All Numeric\\ \hline
%KR-vs-KP	& 36	& 3196	& 0.011	& 48 \%	& All Categorical\\ \hline
%Labor	        & 16	& 57	& 0.281	& 35 \%	& Categorical (8) and Numeric (8)\\ \hline
%Mushroom	& 22	& 8124	& 0.003	& 48 \%	& All Categorical\\ \hline
%Sick	        & 29	& 3772	& 0.008	&  6 \%	& Categorical (23) and Numeric (6)\\ \hline
%Sonar	        & 60	& 208	& 0.288 & 47 \%	& All Numeric\\ \hline
\end{tabular}
\caption{\footnotesize Statistics of the various datasets evaluated in this work.}
\label{table:stats}
\end{table*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

In this section, we conduct experiments to study the feature selection
performances of several well known methods such as Symmetrical
Uncertainty Rank (SUR), Gain Ratio Rank (GRR), Information Gain Rank
(IGR), Correlation Based Rank (CBR), Conditional Entropy Rank (CER)~\cite{guyon_jmlr03}, 
Correlation-based Feature Subset Selection (CFS)~\cite{Hall1998}, 
Reliff (R)~\cite{Robnik-Sikonja2003} , mRMR~\cite{peng2005} and our proposed 
methods: High Recall Expectation (HRE) and High Recall Log likelihood (HRL), 
High Precision Expectation (HPE), High Precision Log likelihood (HPL). 
The first five methods are variable rank methods and the last seven
are subset rank methods. The first five methods are variable rank methods that select variables by ranking them with some metric and the last seven are subset rank methods that assess subsets of variables and consider previous selections to decide the next selection.

{\bf TODO Rodrigo: please update acronyms in plots with those given above,
use MRMR for MRMR... sorry, does not seem sensible to shorten this to 3 letters.}

% TODO: Scott... any interesting things to point out?  
%       Class imbalance / feature-data ratios?

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}[tbp!]
\centering
\includegraphics[width=0.45\textwidth]{./figures/linegraphs/SpectLogisticRegressionRecall.pdf}
\includegraphics[width=0.45\textwidth]{./figures/linegraphs/SpectNaiveBayesRecall.pdf}\\
\includegraphics[width=0.45\textwidth]{./figures/linegraphs/NewsgroupLogisticRegressionRecall.pdf}
\includegraphics[width=0.45\textwidth]{./figures/linegraphs/NewsgroupNaiveBayesRecall.pdf}
\caption{\footnotesize Performance distribution of various feature selection algorithms with samples taken for each dataset, classifier type, and stage of feature selection.}
\label{fig:perf_vs_fs_alg}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

To answer these questions, we first start with
Figure~\ref{fig:perf_vs_dataset}, where we evaluate the performance of
various feature selection algorithms per dataset, averaged across
classifier type and each stage of feature selection.  We observe...
% TODO Scott

In Figure~\ref{fig:perf_vs_classifier}, we examine how well our 
novel feature selection algorithms HRE, HRL, HPE, HPL 
perform vs. classifier, noting that overall performance is best
for Naive Bayes followed by Logistic Regression and noticeably worse for
the SVM --- it seems simply that the probabilistic nature of our feature selection
dovetail best with classification methods that are themselves probabilistic,
and overall best with Naive Bayes which makes the same independence assumptions.
{\bf TODO Rodrigo: can we get bargraphs like those in FeatureSelection classifier,
except only showing HRE, HRL, HPE, HPL *and* averaging over all datasets?
So major group={HRE, HRL, HPE, HPL}, minor group={SVM,LR,NB} and one graph
for each of A/P/R/F.  Also the filename should not have spaces.}

Next we examine Figure~\ref{fig:perf_vs_fs_alg}, where we evaluate the
performance distribution of various feature selection algorithms with
samples taken for each dataset, classifier type, and stage of feature
selection.  Here we see Y.  We observe...

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table*}[tbp!]
\centering
\begin{tabular}{|l|r|r|r|r|l|} \hline
Dataset & \# Features & \# Data & \# Features/\# Data & \% True Labels & Feature Type\\ \hline \hline 
Breast Cancer(BC)	& 9	& 699	& 0.013	& 34 \%	& All Numeric\\ \hline
Diabetes(D)        & 8	& 768	& 0.010	& 35 \%	& All Numeric\\ \hline
Heart Statlog(HS)	& 13	& 270	& 0.048	& 44 \%	& All Numeric\\ \hline
Spect(S)	        & 22	& 80	& 0.275 & 33 \%	& Categorical\\ \hline
Vote(V)	        & 16	& 435	& 0.037	& 39 \%	& Categorical\\ \hline
Newsgroup(NG)	& 500	& 1963	& 0.255	& 49 \%	& All Binary\\ \hline
Horse Colic(HC)	& 22	& 368	& 0.060	& 37 \%	& Categorical (16) and numeric (6)\\ \hline
Credit-American(CR)	& 15	& 690	& 0.022	& 44 \%	& Categorical(9) and numeric (6)\\ \hline
Credit-German(GC)	& 20	& 1000	& 0.020 & 30 \%	& Categorical (13) and Numeric (7)\\ \hline
Hepatitis(H)	& 19	& 155	& 0.123	& 21 \%	& Categorical (13) and Numeric (6)\\ \hline
Ionosphere(I)	& 34	& 351	& 0.097	& 36 \%	& All Numeric\\ \hline
%KR-vs-KP	& 36	& 3196	& 0.011	& 48 \%	& All Categorical\\ \hline
%Labor	        & 16	& 57	& 0.281	& 35 \%	& Categorical (8) and Numeric (8)\\ \hline
%Mushroom	& 22	& 8124	& 0.003	& 48 \%	& All Categorical\\ \hline
%Sick	        & 29	& 3772	& 0.008	&  6 \%	& Categorical (23) and Numeric (6)\\ \hline
%Sonar	        & 60	& 208	& 0.288 & 47 \%	& All Numeric\\ \hline
\end{tabular}
\caption{\footnotesize Statistics of the various datasets evaluated in this work.}
\label{table:stats}
\end{table*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}[tbp!]
\centering
\includegraphics[width=0.375\textwidth]{./figures/linegraphs/SpectLogisticRegressionRecall.pdf}
\includegraphics[width=0.375\textwidth]{./figures/linegraphs/SpectNaiveBayesRecall.pdf}\\
\includegraphics[width=0.375\textwidth]{./figures/linegraphs/NewsgroupLogisticRegressionRecall.pdf}
\includegraphics[width=0.375\textwidth]{./figures/linegraphs/NewsgroupNaiveBayesRecall.pdf}
\caption{\footnotesize Performance distribution of various feature selection algorithms with samples taken for each dataset, classifier type, and stage of feature selection.}
\label{fig:perf_vs_fs_alg}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

In this section, we conduct experiments to study the feature selection
performances of several well known methods such as Symmetrical
Uncertainty Rank (SUR), Gain Ratio Rank (GRR), Mutual Information Rank
(MIR), Correlation Based Rank (CR), Conditional Entropy Rank (CER)~\cite{guyon_jmlr03}, Correlation-based Feature Subset Selection (CS)~\cite{Hall1998}, Reliff (RF)~\cite{Robnik-Sikonja2003} , Minimum Redundancy Maximum Relevancem(MRMR)~\cite{peng2005} and our proposed methods:  Disjunction Voting Expectation(DVE) and  Disjunction Voting likelihood (DVL), Conjunction Voting Expectation (CVE), Conjunction Voting likelihood (CVL). The first five methods are variable rank methods and the last seven are subset rank methods. The first five methods are variable rank methods that select variables by ranking them with some metric and the last seven are subset rank methods that assess subsets of variables and consider previous selections to decide the next selection.

@@

To answer these questions, we first start with
Figure~\ref{fig:perf_vs_dataset}, where we evaluate the performance of
various feature selection algorithms per dataset, averaged across
classifier type and each stage of feature selection. We can observe that our approaches improve recall and accuracy in many of the binary classification problem.
% TODO Scott

In Figure~\ref{fig:perf_vs_classifier}, we examine how well our 
novel feature selection algorithms DVE, DVL, CVE, CVL 
perform vs. classifier, noting that overall performance is best
for Naive Bayes followed by Logistic Regression and noticeably worse for
the SVM Linear --- it seems simply that the probabilistic nature of our feature selection
dovetail best with classification methods that are themselves probabilistic,
and overall best with Naive Bayes which makes the same independence assumptions.

Next we examine Figure~\ref{fig:perf_vs_fs_alg}, where we evaluate the
performance distribution of various feature selection algorithms with
samples taken for each dataset, classifier type, and stage of feature
selection. This graph shows that our high recall feature selection improve recall with improvements noticeable when there is a high feature to data ratio such as in the Newsgroup(NG) and Spect(S) data sets.

### 2014-02-05  feature-selection-high-recall/FeatureSelectionProject/doc/fs_hr/model.tex
Update

Feature selection is the selection of a subset of features $F^*$ from the complete feature space $F,$ for a specific classification/prediction problem, without loosing too much performance on some given measures. The benefit of feature selection include more explainable model, reduced computation time/power, and the avoidance of overfitting.

Existing feature selection algorithms, whose performance show no statistical difference on out benchmark, are mostly ad-hoc. They give various answers to optimisation, but none of them gives the question. In this project, we started from the first principles, proposed a graphical model, and built a new feature selection system upon it.

\subsection{Graphical Model}

To begin the derivation, we propose a graphical model of feature selection for binary classification problem, as shown in figure~\ref{fig:model}. Double-circle nodes represent observed variables, including the data point vector $\vec{x}^{\,d},$ selected features $f_i^*$ (where $1\leq i\leq k,$ $f_i\in F$) and the supervised class label $y^d.$ Single-circle nodes represent latent variables, including a selected attribute of data point vector $f_i^x,$ and prediction from a feature $y^d_i.$

Since jointly optimising this objective is NP-hard, we will build $F^*$ in a greedy manner by choosing the next optimal feature $f^*_k$ given the previous set of optimal features $F^*_{k-1}$ and recursively defining $F^*_k = F^*_{k-1}\cup f^*_k$ with $F^*_0 = \emptyset$. The measure of the fitness of a model can either be Expectation or Likelihood.

\begin{figure}[tbp!]
	\centering
	\includegraphics[scale=0.9]{Plots_1.pdf}
	\caption{Graphical model. Double-wall circle denotes observed nodes, single-wall circle denotes hidden nodes.}
	\label{fig:model}
\end{figure}

\section{Expectation}
The initial objective is defined as:
\[f_k^*=\argmax_{f_k}E_D\left[P\left(y^d|\vec{x}^{\,d},F_k\right)\right]\]

@@

Now we can optimise our initial objective aiming three goals of classification tasks: Precision, Recall, and General n-out-of-k.

@@

\subsection{Likelihood}
\begin{align}
f_k^*&\equiv\argmax_{f_k}\,log\prod_{d\in D}P\left(y^d|\vec{x}^{\,d},F_k\right)\nonumber\\
&=\argmax_{f_k}\sum_{d\in D}log\left(\frac{P\left(y^d,\vec{x}^{\,d},F_k\right)}{P\left(\vec{x}^{\,d},F_k\right)}\right)\nonumber\\
&=\argmax_{f_k}\sum_{d\in D}log\sum_{\{y_i^d\}_{1\leq i\leq k}}\frac{P\left(y^d,\vec{x}^{\,d}, F_k,\{y_i^d\}_{1\leq i\leq k}\right)}{P\left(\vec{x}^{\,d},F_k\right)}\nonumber\\
&=\argmax_{f_k} \sum_{d \in D} log\sum_{{\{y_i^d\}}_{1\leq i \leq k}} \frac{P\left(y^d| \{y^d_i\}_{1 \leq i \leq k}\right) \prod_{i=1}^kP\left(y_i^d|\vec{x}^{\,d},f_i\right)P\left(\vec{x}^{\,d}\right)\prod_{i=1}^kP\left(f_i\right)}{P\left(\vec{x}^{\,d}, F_k\right)}\nonumber\\
&=\argmax_{f_k}\sum_{d\in D}log\sum_{{\{y_i^d\}}_{1\leq i\leq k}}P\left(y^d|\{y^d_i\}_{1\leq i\leq k}\right)\prod_{i=1}^kP\left(y_i^d|\vec{x}^{\,d},f_i\right)\nonumber
\end{align}
Here, we rewrote the likelihood of a binary event as its probability, factorized the conditional probability in the joint probability divided by the marginal, marginalized over $\{y^d_i\}_{1\leq i\leq k}$, factorized joint probability in conditional and prior following the graphical model and exploited d-separation to remove irrelevant conditions and to cancel terms in the equation.

Since $\sum_{d\in D}log\sum_{{\{y_i^d\}}_{1\leq i\leq k}}P\left(y^d|\{y^d_i\}_{1\leq i\leq k}\right)\prod_{i=1}^kP\left(y_i^d|\vec{x}^{\,d},f_i\right)$ is exactly the same as the result in the expectation case, and the logarithm is a monotonous function, the choice of likelihood instead of expectation has no further affect on the algorithm.

>>>>

%Feature selection is the selection of a subset of features $F^*$ from
%the complete feature space $F,$ for a specific
%classification/prediction problem, without loosing too much
%performance on some given measures. The benefit of feature selection
%include more explainable model, reduced computation time/power, and
%the avoidance of overfitting.
%
%Existing feature selection algorithms, whose performance show no
%statistical difference on out benchmark, are mostly ad-hoc. They give
%various answers to optimisation, but none of them gives the
%question. In this project, we started from the first principles,
%proposed a graphical model, and built a new feature selection system
%upon it.

%\subsection{Graphical Model}

In our work, we wish to derive a model of feature selection in the
filtering framework that focuses specifically on recall (we assume the
classifier itself aims to maximize accuracy or some surrogate).  To
begin our derivation, we propose a graphical model of feature
selection for the binary classification problem, as shown in
Figure~\ref{fig:model}. Double-walled nodes represent observed
variables, including the data point vector $\vec{x}^{d},$ selected
features $f_i^*$ (where $1\leq i\leq k,$ $f_i\in F$) and the
supervised class label $y^d.$ Single-walled circle nodes represent
latent (unobserved) variables, including a selected attribute of data
point vector $f_i^x,$ and prediction from a feature $y^d_i.$

Since jointly optimizing this objective is NP-hard, we will build
$F^*$ in a greedy manner by choosing the next optimal feature $f^*_k$
given the previous set of optimal features $F^*_{k-1}$ and recursively
defining $F^*_k = F^*_{k-1}\cup f^*_k$ with $F^*_0 = \emptyset$. The
measure of the fitness of a set of selected features $^*_k$ can be
expressed in terms of log or expected likelihood, derived as follows:

\begin{figure}[tbp!]
	\centering
	\includegraphics[scale=0.9]{Plots_1.pdf}
	\caption{\footnotesize A probabilistic voting model of classification represented as a graphical model. 
Double-walled circles denote observed nodes, single-walled circles denote latent (unobserved) nodes.}
	\label{fig:model}
\end{figure}

%\subsection{Objective}

\COMMENT
\subsubsection{Expected Likelihood}
The initial objective is defined as:
\[f_k^*=\argmax_{f_k}E_D\left[P\left(y^d|\vec{x}^{\,d},F_k\right)\right]\]

@@

Now we can optimise our initial objective aiming three goals of classification tasks: Precision, Recall, and General n-out-of-k.
\ENDCOMMENT

\paragraph{Log Likelihood}

Because Figure~\ref{fig:model} essentially provides a probabilistic classifier model as a function
of the input data and selected features, we can choose features as to maximize the log likelihood
of the data given the model (i.e., features selected), i.e., $l(D|F)$ as follow:

\begin{align}
f_k^*&\equiv\argmax_{f_k} l(D|F^*_k) \nonumber\\
f_k^*&\equiv\argmax_{f_k}\,log\prod_{d\in D}P\left(y^d|\vec{x}^{\,d},F_k\right)\nonumber\\
&=\argmax_{f_k}\sum_{d\in D}log\left(\frac{P\left(y^d,\vec{x}^{\,d},F_k\right)}{P\left(\vec{x}^{\,d},F_k\right)}\right)\nonumber\\
&=\argmax_{f_k}\sum_{d\in D}log\sum_{\{y_i^d\}_{1\leq i\leq k}}\frac{P\left(y^d,\vec{x}^{\,d}, F_k,\{y_i^d\}_{1\leq i\leq k}\right)}{P\left(\vec{x}^{\,d},F_k\right)}\nonumber\\
&=\argmax_{f_k} \sum_{d \in D} log\sum_{{\{y_i^d\}}_{1\leq i \leq k}} \frac{P\left(y^d| \{y^d_i\}_{1 \leq i \leq k}\right) \prod_{i=1}^kP\left(y_i^d|\vec{x}^{\,d},f_i\right)P\left(\vec{x}^{\,d}\right)\prod_{i=1}^kP\left(f_i\right)}{P\left(\vec{x}^{\,d}, F_k\right)}\nonumber\\
&=\argmax_{f_k}\sum_{d\in D}log\sum_{{\{y_i^d\}}_{1\leq i\leq k}}P\left(y^d|\{y^d_i\}_{1\leq i\leq k}\right)\prod_{i=1}^kP\left(y_i^d|\vec{x}^{\,d},f_i\right)\nonumber
\end{align}

Here, we rewrote the likelihood of a binary event as its probability,
factorized the conditional probability in the joint probability
divided by the marginal, marginalized over $\{y^d_i\}_{1\leq i\leq
  k}$, factorized joint probability in conditional and prior following
the graphical model and exploited D-separation to remove irrelevant
conditions and to cancel terms in the equation.

\paragraph{Expected Likelihood}

In contrast to log likelihood which tends to give more weight to extreme
probabilities, we may wish to instead maximize expected likelihood
defined as follows:
\begin{align*}
f_k^*&=\argmax_{f_k}E_D\left[P\left(y^d|\vec{x}^{\,d},F_k\right)\right]\nonumber\\
&=\argmax_{f_k}\frac{1}{|D|}\sum_{d\in D} P\left(y^d | \vec{x}^{\,d},F_k\right)\nonumber\\
&=\argmax_{f_k} \sum_{d\in D} P\left(y^d | \vec{x}^{\,d},F_k\right)\nonumber\\
\end{align*}
If we remove the logarithm from the previous derivation above, we easily
derive the final result of the log likelihood, except without the logarithm.

%Since $\sum_{d\in D}log\sum_{{\{y_i^d\}}_{1\leq i\leq
%    k}}P\left(y^d|\{y^d_i\}_{1\leq i\leq
%  k}\right)\prod_{i=1}^kP\left(y_i^d|\vec{x}^{\,d},f_i\right)$ is
%exactly the same as the result in the expectation case, and the
%logarithm is a monotonous function, the choice of likelihood instead
%of expectation has no further affect on the algorithm.

\paragraph{Voting Schemes for High Recall}

Critically, it is how we specify the model and objective that we
believe should encourage feature selection with high recall.  
In the following we focus on ***

@@

### 2014-02-05  feature-selection-high-recall/FeatureSelectionProject/doc/fs_hr/related_work.tex
Updated empirical results
Update

\section{Related Work}

Existing feature selection algorithms fall into categories of filter
methods and wrapper methods \cite{guyon_jmlr03}. While
wrapper methods, such as SVM-RFE \cite{guyon2002gene}, select features
by evaluating their usefulness to a given classifier, filter methods
evaluate feature subsets according to certain properties of
themselves. Within filter methods, feature selection algorithms can be
further classified into ranking methods and subset methods. The former
evaluates each features independently, while the latter evaluates a
subset at a time \cite{brown2012conditional}. Listed below is a brief
introduction to algorithms to which we compared our proposed model.

@@

Correlation based subset \cite{Hall1998} is an extension
of Pearson's $r$ to subset methods. It measures the linear correlation
between each pair of selected features in addition to the correlation
between selected features and the output class. The other subset
algorithm to which we compared our work is MRMR \cite{peng2005}.
MRMR is an information-theory-based method that not only maximises
the relevance of selected features to the supervised output class,
but also minimises the redundancy among selected features. Different
search strategies can be applied using these two algorithms as
heuristics.

Although existing algorithms give various solutions, they are mostly
ad-hoc, until \cite{brown2012conditional}. Brown et al.\ derived an
information-theoretical model from first principles, and retro-fitted
existing information-theory-based feature selection methods to the
model. In this paper, we consider the other side of the same coin. We
proposed a probability-theory-based graphical model that has intuitive
qualitative meaning in precision and recall, and we built a
generalized feature selection scheme upon it.

>>>>

\section{Existing Feature Selection Algorithms}

Existing feature selection algorithms fall into categories of filter
methods and wrapper methods \cite{guyon_jmlr03}. While
wrapper methods, such as SVM-RFE \cite{guyon2002gene}, select features
by evaluating their usefulness to a given classifier, filter methods
evaluate feature subsets according to certain properties of features 
themselves. Within filter methods, feature selection algorithms can be
further classified into ranking methods and subset methods. The former
evaluate each feature independently, while the latter evaluate a
subset at a time \cite{brown2012conditional}. Listed below is a brief
introduction to popular feature selection algorithms that we later
compare to.

@@

Correlation-based subset \cite{Hall1998} is an extension
of Pearson's $r$ to subset methods. It measures the linear correlation
between each pair of selected features in addition to the correlation
between selected features and the output class. The other subset
algorithm to which we compared our work is MRMR \cite{peng2005}.
MRMR is an information-theoretic method that not only maximizes
the relevance of selected features to the supervised output class,
but also minimizes the redundancy among selected features. Different
search strategies can be applied using these two algorithms as
heuristics.

Although existing algorithms give various solutions, they are mostly
ad-hoc, until \cite{brown2012conditional}. Brown et al.\ derived a 
probabilistic model with information-theoretic motivations from first principles, and retro-fitted
existing information-theory-based feature selection methods to the
model. In this paper, we also take a derivational approach to
specifying a probabilistic model and optimizing a feature selection
objective w.r.t. that model, but in our case we focus on the specific
task of optimizing for recall in binary classification, which it 
seems no prior method has focused on in previous work.
